Deciding to Disclose

### 2015-06-22 model_description.tex
Adding to the construction

Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

Midwives are treated in a similar fashion, where their type corresponds to how negatively they regard a drinking pattern - non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response, which is to either refer the woman for specialist treatment, or do nothing.

>>>>

At this point, the game becomes challenging to analyse from a Nash equilibrium perspective (there are several hundred). But, having raised to issue of stigma, we would also like incorporate this in the game. A possible approach to this is similar to the drinking behaviour of the women, and lets midwives have a type as well, corresponding to how judgemental they are when receiving signals: non-judgemental, moderately judgemental, and harshly judgemental. The expression of this judgement is not a matter of choice on their part, and is assumed to have no impact on their clinical response. Nature now has an additional move, to choose the type of the midwife, and we add costs for sending moderate and heavy signals. A heavy signal to a harshly judgemental midwife adds a heavy cost, and a moderate cost from a moderate midwife. The resulting game might reasonably be said to be intractable.

At this juncture, we do not gain much further from the game representation, and instead separate it into multiple decision problems.
